\documentclass[]{article}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage[a4paper,margin=20mm]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
    citecolor=black
}
\urlstyle{same}
\begin{document}
\title{UCL Film and TV Society Studio and Equipment Handbook}
\author{HD - Studio and Equipment Manager}
\date{\today}
\maketitle
\tableofcontents
\section{Introduction}
Hello and thank you for taking the time to read our Studio and Equipment Rules. These rules must be followed when using any of UCL Film and TV Society's spaces or equipment. If you have any questions or concerns, please get in touch with:
\begin{itemize}
    \item Studio and Equipment Managers
          \begin{itemize}
              \item Hasha Dar (HD) - \href{mailto:hasha.dar.19@ucl.ac.uk}{hasha.dar.19@ucl.ac.uk}
              \item Jamie Wong - \href{mailto:jamie.wong.19@ucl.ac.uk}{jamie.wong.19@ucl.ac.uk}
          \end{itemize}
    \item Senior Committee
          \begin{itemize}
              \item Diego Collado - \href{mailto:diego.collado.19@ucl.ac.uk}{diego.collado.19@ucl.ac.uk}
              \item Saul Lotzof - \href{mailto:saul.lotzof.20@ucl.ac.uk}{saul.lotzof.20@ucl.ac.uk}
          \end{itemize}
\end{itemize}
\subsection{Definitions}
\begin{enumerate}
    \item `The Society' - the University College London Film \& TV Society
    \item `K' (e.g. 1K) - short form for `thousand'. A 1K light refers to a lantern with a rated power output of \SI{1000}{\watt}
    \item `SEM' - Studio (and) Equipment Manager
\end{enumerate}
\subsection{Prerequisites}
Before you can book/use the studio and equipment, you \textit{must} be:
\begin{itemize}
    \item A full `production' member of The Society. You may be asked to provide your name and email address to us to cross-check your membership on our systems.
    \item Eligible to book studio/equipment (see \nameref{strikeSystem}).
\end{itemize}
\section{Studio}
\subsection{The space}\label{studioSpaces}
The studio is located in the Bloomsbury Theatre Building on the right side of the building. Entering via the Bloomsbury Theatre North entrance, the studio can be located at the end of the corridor and down the flight of stairs. Access may also be obtained via the lift. Studio access may only be achieved via a ID card of a committee member. The studio itself is divided up into three main sections, each of which can be booked individually.
\begin{enumerate}
    \item Main studio
    \item Sound recording room
    \item Post-production room
\end{enumerate}
\subsection{Rules on bookings}
\begin{enumerate}
    \item Bookings must be made at least 48 hours in advance of the start time of your booking.
    \item You may only make bookings for the studio up until the date that the current term ends. Bookings for the next term shall open on the day that the previous term ends.
    \item Bookings hours are dependent on the times that the Bloomsbury Theatre Building is open. This is typically 9:00 - 22:00 on weekdays and 9:00 - 18:00 on weekends. This may be subject to change and out of control of The Society.
    \item Availability of studio space is at the discretion of the SEMs and Senior Committee. A booking may be cancelled at any time by a member of the Senior Committee or a SEM. Reasons for cancellation may include:
          \begin{itemize}
              \item Documentary or Term Film production precedence
              \item Consequence of strikes (see \nameref{strikeSystem})
          \end{itemize}
    \item As the sound recording room requires that activity in the post-production room be silent, concurrent bookings of the sound recording room and post-production room shall not be made. This is to ensure that adequate work may take place in each space. An SEM may discretionally book both spaces, if the circumstances allow.
\end{enumerate}
\subsection{How to make a booking}
To make a booking, please get in touch with HD or Jamie (SEMs). Alternatively, you may get in touch with us via social media or email. We aim to respond within 1-2 working days, hence booking up to a week in advance is preferable (to ensure that you have enough time to find an alternative venue if the studio is not available). In your request, you \textit{must} include:
\begin{itemize}
    \item Date, start and end times of your booking.
    \item Which room you would like to book in the studio (see list in \ref{studioSpaces}).
    \item Project name + purpose of booking
    \item Equipment needed (if any - see \nameref{equipment}).
\end{itemize}
If the above are not included in your enquiry, it will only delay confirming your booking, please ensure that you have an accurate idea of the dates and times of your booking (and what equipment/facilities you require).
\subsection{Studio use and etiquette}
\begin{enumerate}
    \item The studio is a shared space managed by the The Society. Please be considerate of other users in the space.
    \item Please ensure that you arrive on time for your booking. If you are late for your booking, please inform a SEM as soon as possible. If you find yourself at the Studio and no one is there to unlock the door, you should call a SEM (whose number shall be provided to you once a booking is confirmed).
    \item When your booking has finished, please ensure to leave enough time to restore the studio back to a clean and ordered state (as you would like to find it). This includes stacking chairs and restoring furniture to its original position, sweeping the floor, packing away props and equipment etc.
    \item Only SEM or Senior Committee member may assess whether the studio space has been left in a clean state.
    \item If there are any accidents, spills, or damage to the studio space, a committee member \textit{must} be informed as soon as possible (ideally a SEM). We handle all incidents on a case-by-case basis according to Students' Union procedure.
\end{enumerate}
\section{Equipment}\label{equipment}
The has an inventory of equipment kept in the studio. Production members of the society may book this equipment out for personal shoots. Booking equipment is free of charge.

Equipment booking inquiries are subject to varying degrees of scrutiny. You may be asked to provide a brief overview as to why you require certain equipment. You may also be asked to provide a production schedule, if booking for longer periods of time. Equally, you may ask a SEM for advice on which equipment they think would work best for your shoot or use case.

Some equipment may require prior training before use. If you require use of such equipment, then a SEM shall arrange for such training to take place or assess your current skill level.
\subsection{Current list of equipment}
Equipment which requires training as a prerequisite is marked with an asterisk.
\begin{itemize}
    \item Cameras
          \begin{itemize}
              \item Blackmagic Pocket Cinema Camera 6K*
              \item Blackmagic Pocket Cinema Camera 4K*
              \item Canon C100*
              \item JVC 4K Camcorder*
              \item Sony A7 Mirrorless Camera*
          \end{itemize}
    \item Camera Miscellaneous
          \begin{itemize}
              \item Cinema Prime Lenses (14mm, 23mm, 35mm, 50mm, 85mm, 105mm)*
              \item Zoom lens (24-105mm)
              \item VLok batteries
              \item Camera batteries
              \item Carrying bag
              \item Various connection cables (Video, Power)
          \end{itemize}
    \item Sound
          \begin{itemize}
              \item Zoom H6 recorder*
              \item Rode boom mic (x2)
              \item Boom pole (x2)
              \item Shock mount for boom pole + protective cover + dead cat (x2)
              \item Condenser mic
              \item USB condenser mic
              \item Sennheiser lavalier radio mic set
              \item XLR cables
          \end{itemize}
    \item Tripods and stands
          \begin{itemize}
              \item Manfrotto 504
              \item Manfrotto 504X
              \item Manfrotto 504HD
              \item Manfrotto monopod
              \item Manfrotto slider
              \item Velbon EF-61 (x2)
              \item C-stands + knuckles + extension poles*
          \end{itemize}
    \item Lighting
          \begin{itemize}
              \item Falcon Eyes LED panel*
              \item 1K light*
              \item Kinoflo*
              \item Gels and soft frost
              \item Lighting flags*
          \end{itemize}
    \item Storage
          \begin{itemize}
              \item SD cards
              \item SSD drives
          \end{itemize}
\end{itemize}
\subsection{Rules on bookings}
\begin{enumerate}
    \item Booking must be made at least 48 hours in advance of the start time of your booking.
    \item You may only make bookings for equipment up until the date that the current term ends. Bookings for the next term shall open on the day that the previous term ends.
    \item Equipment rentals are at the discretion of the committee. A booking may be cancelled at any time by a member of the Senior Committee or a SEM. A cancellation whilst kit is booked out will require that kit be returned within 24 hours (ideally ASAP). Reasons for cancellation may include:
          \begin{itemize}
              \item Documentary or Term Film production precedence
              \item Consequence of strikes (see \nameref{strikeSystem})
          \end{itemize}
    \item Care of the equipment whilst booked out is the responsibility of the person making the booking. Kit must be checked out by a SEM or a member of the Senior Committee.
    \item Kit being returned to the studio \textit{must} receive the approval of a SEM or member of Senior Committee. This approval may be verbal (in-person) or as a text (if \textbf{all} the equipment is confirmed to be returned to the studio.) Only photographic evidence may be deemed as proof of return (if a SEM/Senior Committee Member is not there to assist in check-in of equipment).
    \item Storage items should be given to you pre-formatted. If you find you have been given a card which has data on it, please contact a SEM, who shall assist you. Upon returning a card, please ensure that all important data has been copied by you. Upon check-in of a storage media, we can no longer guarantee that you may retrieve any data that you may have had on it. You may not keep the storage item beyond your allocated booking period.
\end{enumerate}
\subsection{How to make a booking}
To make a booking, please get in touch with HD or Jamie (SEMs). Alternatively, you may get in touch with us via social media or email. We aim to respond within 1-2 working days, hence booking up to a week in advance is preferable (to ensure that you have enough time to find an alternative (if the equipment you require is not available). In your request, you \textit{must} include:
\begin{itemize}
    \item Date, start and end times of your booking.
    \item Equipment needed.
    \item Project name + purpose of booking
    \item Production schedule (may be requested by SEM)
\end{itemize}
If the above are not included in your enquiry, it will only delay us in confirming your booking, please ensure that you have an accurate idea of the dates and times of your booking (and what equipment/facilities you require).
\subsection{Equipment use and etiquette}
The Society is the owner of all property mentioned above and is subject to UCL Students' Union inventory policy. All equipment is insured and kept secured in the The Society storage facilities.
\begin{enumerate}
    \item Any incidents/damage to equipment \textit{must} be reported ASAP. Damage assessment and repair cost quote is the sole responsibility of the SEM. No attempts to repair the equipment should be made by anyone other than those who receive the express approval of a SEM.
    \item All damages are assessed on a case-by-case basis. For small damages, you may be billed directly. For larger damages, insurance policies protect you and our equipment.
    \item Please return all equipment promptly and on time.
\end{enumerate}
\section{Strike system}\label{strikeSystem}
To ensure smooth operation, we have a strike system in place. For breaching the rules aforementioned, one may receive a `strike'. Strikes impact whether studio time or equipment is given.

If one is to receive three strikes, they will be barred from all space and equipment bookings. Receiving three strikes will not be considered as grounds to approve a request to refund The Society production membership.
\end{document}